---
title: "Tutorial 1 DSA2101"
author: "Waseem"
date: "11/10/2021"
output: pdf_document
---
1. There are missing values in the tables. Inspect the tables carefully and fill them in. The new arrests
object should be free of NA values.
```{r echo = TRUE}
arrests <- readRDS("data/arrests.rds")
sapply(arrests,function(x) any(is.na(x[[1]])) || any(is.na(x[[2]])))

arrests[['2011']]$age$Female[1] <- 2992 +1125 + 1008
arrests[['2019']]$age$Male[2] <- 9920 + 3208 + 10465

```
2. In the DataCamp R markdown course, you learnt about kable from the knitr package. Use it to display the tables for 2019:
```{r echo = TRUE}
library(knitr)
kable(arrests[["2019"]],
row.names= NA,
col.names= c('Citizenship status', 'Male', 'Female' ))
```
3. Retrieve the citizenship table from 2011 to 2015 inclusive and store it in a list object called qn3_list.
```{r echo = TRUE}
qn3_list<-lapply(arrests[1:5],function(x) x$citizenship)
```
4. Compute the total number of arrests in each year, and store them in a numeric vector qn4_vec.
```{r echo = TRUE}
qn4_vec<- sapply(arrests,function(x) sum( x[[1]][,-1]))
```
5. Use qn4_vec to retrieve and store only those years’ data where the total number of arrests was less
than 18000, but more than 17000. Store them in qn5_list.
```{r echo = TRUE}
qn5_list <- arrests[qn4_vec <18000 & 17000 > qn4_vec ]

```
6. Measure of association I: When we deal with 2x2 tables, one measure of association between the
variables is the difference in proportions. Write a function prop_diff that takes in one of the data frames and returns the difference between proportion of Males for each row.
```{r echo = TRUE}
x<-arrests[[1]][[1]]
prop_diff<- function(x){
(x[[2]][[1]]/(x[[2]][[1]]+x[[3]][[1]]))-(x[[2]][[2]]/(x[[2]][[2]]+x[[3]][[2]]))

}

qn6.1_vec <- sapply(arrests,function(y) prop_diff(y[[1]]))
qn6.2_vec <- sapply(arrests,function(y) prop_diff(y[[2]]))
qn6_df <- data.frame (qn6.1_vec,qn6.2_vec)
qn6_df

```
7. Compute the log-odds ratio for each data.frame and store them in a data.frame called qn7_df, with one row for each year.

```{r echo = TRUE}
bob <- function (x){
log(x[[2]][[1]] * x[[3]][[2]]) / ( x[[2]][[2]] * x[[3]][[1]])

}
qn7.1_vec <- sapply(arrests,function(y) bob(y[[1]]))
qn7.2_vec <- sapply(arrests,function(y) bob(y[[2]]))
qn7_df <- data.frame (qn7.1_vec,qn7.2_vec)
qn7_df

```