---
title: "Tutorial 5 Worksheet AY 21/22 Sem 1"
output: 
  pdf_document: default
---
Read your data into R as absent and identify the number of couriers in the dataset.
``` {r echo = TRUE}
library(readr)
library(tidyverse)
absent <- read_delim("data/Absenteeism_at_work.csv")
absent_count<-select(absent,ID) %>% 
   unique() %>% 
   count()
absent_count
```
1.There are 36 couriers in the dataset.

2.Max absences
Obtain the longest 7 absences (with ties equals TRUE). Keep only the courier ID, reason for absence and the Absenteeism time. Make a mental note of the couriers you observe.
Courier IDs-14,36,9,28,9,11,36
```{r echo=TRUE}
max_absence_tbl<-select (absent , "ID", "Reason for absence" , "Absenteeism time in hours" )
max_absence_tbl<-slice_max(max_absence_tbl,order_by=max_absence_tbl$`Absenteeism time in hours`,n=7)
max_absence_tbl
```

Unknown reason for absence

Extract the rows corresponding to reason for absence equals to 0. Keep only the ID, reason for absence, discipline record and absenteeism time. What do you observe?
Courier IDs of first 10 - 36,20,28,11,26,13,36,2,7,18.
Courier 36,28,11, were in the list of the longest 7 absences, and also have corresponding readon for absence equals to 0. Maybe there is a correlation. 
```{r echo=TRUE}
reason_tbl<-select(absent, "ID","Reason for absence","Disciplinary failure","Absenteeism time in hours")
reason_tbl<-filter(reason_tbl, reason_tbl$`Reason for absence`==0)
reason_tbl

```
Remove disciplinary failure
Remove the rows corresponding to disciplinary failure equals to 1.
```{r echo=TRUE}
absent <- filter(absent, absent$`Disciplinary failure` !=1)
absent
```
Recode day of week and season
Recode the columns Day.of.the.week and Seasons to the character values given above. Here are some example rows and columns.
```{r echo=TRUE}
absent$`Day of the week`<-recode(absent$`Day of the week`, '2'="Mon","3"="Tue","4"="Wed","5"="Thu","6"="Fri")
absent$Seasons<-recode(absent$Seasons, "1"="Summer","2"="Autumn","3"="Winter","4"="Spring")
absent
```
Proportion of absences in Day by Season
Create a tibble that shows the proportion of absences in each season that occur on each weekday. Here are some of the rows in my dataset:
A tibble named absence_props show- ing the proportion of absences that took place on a particular weekday within a season.

```{r echo=TRUE}

absence_props<-absent %>%
   group_by(Seasons,`Day of the week`) %>%
   count() %>%
   group_by(Seasons) %>%
   mutate(prop= n/sum(n)) %>% 
   ungroup()
absence_props
```
Summaries by courier
For each courier, compute the following summary statistics: min, max, median, lower quartile, upper quartile, total absence time and total number of absences. Who are the most dilligent couriers? Who are the least?

Couriers 4 and 35 are the most diligent as they have only been absent once, whereas Couriers 3 and 38 have been absent for 113 and 77 times respectively. 
```{r echo=TRUE}
statistic<- function(x){
   q_df<-as.data.frame(t(quantile(x)))
   colnames(q_df)<-c ("min","lower","median","upper","max")
   q_df$abs_time <- sum(x)
   q_df$abs_count<- length(x)
   q_df
}
courier_summary<- absent %>% group_by(ID) %>% 
   summarise(statistic(`Absenteeism time in hours`),.groups="drop")
courier_summary

```
Status Changes
The following demographic variables could have changed over the three years for which the couriers were tracked: Education to Pet status (five columns).
Use dplyr to investigate which of the couriers’ status changed over the three years.

Since there are no rows from the code run below, the couriers status have not changed over the three years. 
```{r echo =TRUE}
helper<-function(x){
   change <- length(unique(x)) !=1
   change
}
absent %>% 
   group_by(ID) %>%
   summarise(across(.cols=c(Education:Pet,`Body mass index`),helper)) %>%
   ungroup() %>%
   rowwise() %>%
   mutate(any_change=any(c_across(-1))) %>% 
   filter(any_change)
```